Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-04-13 ltx/BrainIDE.tex
some more changes and aded the guide for journal of neuroeng

\boldsymbol{\Sigma}_w=\boldsymbol{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \rho\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top} 

@@

\rho\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\

@@

Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited. Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}. In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field. Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually band-limited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency. Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$. Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$. Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.

@@

Similar considerations need to be made regarding the representation of the dynamic field $w_t(\mathbf{r})$ by its basis functions decompositions. The minimum distance between adjacent basis functions needs to again satisfy Shannon's sampling theorem. Thus the minimum distance between basis must again satisfy $\frac{1}{2\nu_c}$. For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}. The Fourier transform of a Gaussian is another Gaussian with width $\sigma^2_{\nu}$ given by $\sigma^2_{\nu} = \frac{1}{\pi^2\sigma^2}$. Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with the 3dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma^2$.

>>>>

\boldsymbol{\Sigma}_w=\boldsymbol{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf{r}- \mathbf{r}' \right)\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf{r}\boldsymbol{\Gamma}^{- \top} 

@@

\gamma\left(\mathbf{r}-\mathbf{r'}\right), & \tau=0 \\

@@

Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited. Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}. In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field. Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually band-limited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency. Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$. Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within
\begin{equation}
		\Delta_s = \frac{1}{2\rho\nu_c}
\end{equation}
 $\frac{1}{2\nu_c}$. Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.

@@

Similar considerations need to be made regarding the representation of the dynamic field $w_t(\mathbf{r})$ by its basis functions decompositions. The minimum distance between adjacent basis functions needs to again satisfy Shannon's sampling theorem. Thus the minimum distance between basis must again satisfy 
\begin{equation}
	\Delta_b = \frac{1}{2\rho\nu_c}.
\end{equation}
For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}. The Fourier transform of a Gaussian is another Gaussian with width $\sigma^2_{\nu}$ given by $\sigma^2_{\nu} = \frac{1}{\pi^2\sigma^2}$. Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with the 3dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma^2$.
